### 2019-06-11 prod/paper/paper_draft.tex
first draft paper

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Insert your title here%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Bobak Farzin         \and
        Second Author %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{bfarzin@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: 15 June 2019 / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Included citations as necessary: ~\cite{Nobody06}
\section{Task and Dataset Description}
\label{sec:task}
The \textit{Humor Analysis based on Humor Annotation (HAHA)} competition asked for analysis of two tasks in the Spanish language based on a coprpus of publicly collected data ~\cite{castro2018crowd}:
\begin{itemize}
\item \textbf{Task1: Humor Detection}:Detemine if a tweet is humorous. System ranking is based on F1 score which will balance precision and accuracy.
\item \textbf{Task2: Funniness Score}:If humorous, what is the average humor rating of the tweet. System ranking is based on RMSE.
\end{itemize}
HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons) and a True/False labels as well as a ``Funninness Score'' that is the average of the 1 to 5 start votes cast.  Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/}.

\section{System Description}
\label{sec:system}
We follow the method of ULMFiT ~\cite{DBLP:journals/corr/abs-1801-06146} and train a language model based on a larger corpus.

Since we are working with Twitter data, we collected 475,143 tweets in the spanish lanugage using tweepy ~\cite{tweepy}.
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Data and Cleanup}
\label{sec:cleaning}

Using sentencepiece~\cite{DBLP:journals/corr/abs-1808-06226} to parte into sub-word units,

Clean by removing the new-line character \verb|\n| in each of the tweets and replacing with \verb|xxnl|.

Use standard pre-processing rules (show example of cleaned up text):

Original:
\begin{verbatim} 
Saber, entender y estar convencides que la frase 
#LaESILaDefendemosEntreTodes es nuestra linea es nuestro eje.
#AlertaESI!!!!
Vamos por mas!!! e invitamos a todas aquellas personas que quieran 
se parte.
\end{verbatim}

Cleaned up:
\begin{verbatim} 
xxbos saber , entender y estar convencides que la frase 
# laesiladefendemosentretodes es nuestra linea es nuestro eje.
xxnl  # alertaesi xxrep 4 ! xxnl vamos por mas ! ! ! e invitamos a 
todas aquellas personas que quieran se parte.
\end{verbatim}

oversample minority class to balance for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}

\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

\section{Experiments and Results}
\label{sec:4}

\section{Conclusion}
\label{sec:4}

\section*{Acknowlegements}
% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{llll}
\hline\noalign{\smallskip}
first & second & third & fourth \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.

% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{local}   % name your BibTeX data base

% Non-BibTeX users please use
%\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
%\bibitem{RefJ}
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%\bibitem{RefB}
%Author, Book title, page numbers. Publisher, place (year)
% etc
%\end{thebibliography}

\end{document}
% end of file template.tex

### 2019-06-12 prod/paper/paper_draft.tex
adding more detail to paper

@@
 Included citations as necessary: ~\cite{Nobody06}
+\paragraph{Contribution} Our contribution with this work is..
+
 \section{Task and Dataset Description}
@@
 \label{sec:system}
-We follow the method of ULMFiT ~\cite{DBLP:journals/corr/abs-1801-06146} and train a language model based on a larger corpus.
 
-Since we are working with Twitter data, we collected 475,143 tweets in the spanish lanugage using tweepy ~\cite{tweepy}.
-Text with citations \cite{RefB} and \cite{RefJ}.
-\subsection{Data and Cleanup}
-\label{sec:cleaning}
+We generally follow the method of ULMFiT ~\cite{DBLP:journals/corr/abs-1801-06146}
+\begin{enumerate}
+	\item Train a language model (LM) on a large corpus of data
+	\item Fine-tune the LM based on the target task language data
+	\item Replace the final layer of the LM with a softmax or linear output layer and then fine-tune on the particular task at hand (classification or regression)
+\end{enumerate}
+Below we will give more detail on each step and the parameters used to generate our system.
+\subsection{Data, Cleanup \& Tokenization}
+\label{sec:datacleaning}
+\subsection{Additional Data}
+For our initial training, we  collected 475,143 tweets in the Spanish language using tweepy ~\cite{tweepy}.
+The vocabulary and frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is used to train.
 
-Using sentencepiece~\cite{DBLP:journals/corr/abs-1808-06226} to parte into sub-word units,
+We combined the labeled and un-labeled text data so that we have the largest corpus of language for our fine-tuning step.
 
-Clean by removing the new-line character \verb|\n| in each of the tweets and replacing with \verb|xxnl|.
+\subsection{Cleaning}
+We applied a list of default cleanup functions included in Fastai and added an additional one for this Twitter dataset.
+\begin{itemize}
+	\item Add spaces between special chars (ie. \verb|!!!| to \verb|! ! !|)
+	\item Remove useless spaces (remove more than 2 spaces in sequence)
+	\item Replace repetition at the character level (ie. \verb|grrrreat| becomes \verb|g xxrep r 3 eat|)
+	\item Replace repition at the word level (similar to above)
+	\item Deal with ALL CAPS words replacing with a token and converting to lower case.
+	\item \textbf{NEW:} Move all text onto a single line by replacing new-lines inside a tweet with a reserved word (ie. \verb|\n| to \verb|xxnl|)
+\end{itemize}
 
-Use standard pre-processing rules (show example of cleaned up text):
+\pagebreak  %move as needed to keep tweet text together
+Here is an example of replacing the original tweet with our parsed version.
 
@@
 \begin{verbatim} 
-Saber, entender y estar convencides que la frase 
-#LaESILaDefendemosEntreTodes es nuestra linea es nuestro eje.
+Saber, entender y estar convencides que la frase \
+#LaESILaDefendemosEntreTodes es nuestra linea es nuestro eje.\
 #AlertaESI!!!!
-Vamos por mas!!! e invitamos a todas aquellas personas que quieran 
+Vamos por mas!!! e invitamos a todas aquellas personas que quieran \
 se parte.
@@
 \begin{verbatim} 
-xxbos saber , entender y estar convencides que la frase 
-# laesiladefendemosentretodes es nuestra linea es nuestro eje.
-xxnl  # alertaesi xxrep 4 ! xxnl vamos por mas ! ! ! e invitamos a 
+xxbos saber , entender y estar convencides que la frase \
+# laesiladefendemosentretodes es nuestra linea es nuestro eje.\
+xxnl  # alertaesi xxrep 4 ! xxnl vamos por mas ! ! ! e invitamos a \
 todas aquellas personas que quieran se parte.
@@
 
+\subsection{Tokenization}
+We used sentencepiece~\cite{DBLP:journals/corr/abs-1808-06226} to parse into sub-word units and reduce the possible out-of-vocabulary (OOV) terms in the data set.
+We selected a vocab size of 30,000 sub-word units and got 99.95\% character coverage including emojis.
+
+\section{Training and Results}
+\label{sec:4}
+LM: 10\% validation set for training
+
 oversample minority class to balance for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}
 
-\paragraph{Paragraph headings} Use paragraph headings as needed.
-\begin{equation}
-a^2+b^2=c^2
-\end{equation}
-
-\section{Experiments and Results}
-\label{sec:4}
+\subsection{Random Seed as a Hyperparamter}
 
 \section{Conclusion}
-\label{sec:4}
+\label{sec:5}
 
@@
 
-% Non-BibTeX users please use
-%\begin{thebibliography}{}
-%
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-%\bibitem{RefJ}
-% Format for Journal Reference
-%Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-%\bibitem{RefB}
-%Author, Book title, page numbers. Publisher, place (year)
-% etc
-%\end{thebibliography}
-
 \end{document}

### 2019-06-12 prod/paper/paper_draft.tex
fixing author title area
update of paper

@@
 %
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
+
 %
@@
 %\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
 %\documentclass[twocolumn]{svjour3}          % twocolumn
@@
 
-%\titlerunning{Short form of title}        % if too long for running head
+\titlerunning{Short form of title}        % if too long for running head
 
-\author{Bobak Farzin         \and
-        Second Author %etc.
+\author {\textbf{Bobak Farzin$^1$}, \textbf{Nombre Apellidos2$^2$}\\
+	$^1$bfarzin@gmail.com\\
+	$^2$Universidad o lugar de trabajo\\
 }
 
-%\authorrunning{Short form of author list} % if too long for running head
+%\author{Bobak Farzin         \and
+%        Second Author %etc.
+%}
 
-\institute{F. Author \at
-              first address \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
-              \email{bfarzin@gmail.com}           %  \\
+\authorrunning{Short form of author list} % if too long for running head
+
+%\institute{F. Author \at
+%              first address \\
+%              Tel.: +123-45-678910\\
+%              Fax: +123-45-678910\\
+%              \email{bfarzin@gmail.com}           %  \\
 %             \emph{Present address:} of F. Author  %  if needed
-           \and
-           S. Author \at
-              second address
-}
+%           \and
+%           S. Author \at
+%              second address
+%}
 
@@
 \label{sec:system}
-
 We generally follow the method of ULMFiT ~\cite{DBLP:journals/corr/abs-1801-06146}
@@
 \subsection{Additional Data}
-For our initial training, we  collected 475,143 tweets in the Spanish language using tweepy ~\cite{tweepy}.
-The vocabulary and frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is used to train.
+For our initial training, we  collected 475,143 tweets in the Spanish language using tweepy ~\cite{Tweepy}.
+The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is used to train.
 
 We combined the labeled and un-labeled text data so that we have the largest corpus of language for our fine-tuning step. 
-
 \subsection{Cleaning}
@@
 	\item Deal with ALL CAPS words replacing with a token and converting to lower case.
-	\item \textbf{NEW:} Move all text onto a single line by replacing new-lines inside a tweet with a reserved word (ie. \verb|\n| to \verb|xxnl|)
+	\item \textbf{Addition:} Move all text onto a single line by replacing new-lines inside a tweet with a reserved word (ie. \verb|\n| to \verb|xxnl|)
 \end{itemize} 
-
 \pagebreak  %move as needed to keep tweet text together
-Here is an example of replacing the original tweet with our parsed version.
-
-Original:
+The following example shows the application of this data cleaning to a single tweet:
 \begin{verbatim} 
@@
 
-Cleaned up:
 \begin{verbatim} 
@@
 \subsection{Tokenization}
-We used sentencepiece~\cite{DBLP:journals/corr/abs-1808-06226} to parse into sub-word units and reduce the possible out-of-vocabulary (OOV) terms in the data set.
-We selected a vocab size of 30,000 sub-word units and got 99.95\% character coverage including emojis.
+We used sentencepiece~\cite{SentencePiece:DBLP:journals/corr/abs-1808-06226} to parse into sub-word units and reduce the possible out-of-vocabulary (OOV) terms in the data set.
+We selected a vocab size of 30,000 and used the byte-pair encoding (bpe) model.
 
@@
 \label{sec:4}
-LM: 10\% validation set for training
 
-oversample minority class to balance for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}
+\subsection{LM Training and Fine-tuning}
+With our data cleaned and tokenized we move to training the LM using a 90/10 training/validation split.
+For the LM, we selected a AWD\_LSTM \cite{} model included in Fastai with QRNN units, 2304 hidden-states, 3 layers and a softmax layer on the end to predict the next-word.
+We tied the embedding weights on the encoder and decoder for training.
+We performed some simple tests with LSTM units and with a Transformer Language model and found all the models were similar in performance during LM training.
+We chose the QRNN units to speed up training.
+The model has about 60 million trainable parameters.
+
+Both the LM and the Classifer models used label smoothing \cite{labelsmooth} of the flattened cross-entropy loss.
+With the classifier, this allowed us to train without gradual unfreezing of the layers as discussed in \cite{HowarRuder:DBLP:journals/corr/abs-1801-06146}
+Parameters used for training all networks can be found in \ref{tab:tab_training}.
+For all the networks we applied a dropout multiplier that scales the dropout used throughout the network.  We used the Adam optimizer with weight decay as indicated in the table.
+
+Following the work of \cite{smith}  we found the largest learning-rate that we could apply and then ran a one-cycle policy \cite{} for a single epoch.
+We then ran subsequent training with lower learning rates, again indicated in \ref{tab:tab_training}.
+
+\begin{table}[ht]
+	% table caption is above the table
+	\caption{LM Training Parameters}
+	\label{tab:tab_training}       % Give a unique label
+\begin{tabular}{lll}
+	\hline\noalign{\smallskip}
+	Param & LM & Fine-Tune LM \\
+	\noalign{\smallskip}\hline\noalign{\smallskip}
+	Weight Decay & 0.1 & 0.1 \\
+	Dropout Mult & 1.0 & 1.0 \\
+	Learning Rate & 1 epoch at $5*10^{-3}$ & 5 epochs at $3*10^{-3}$ \\
+    Cont. Training & 15 epochs at $1*10^{-3}$ & 10 epochs at $1*10^{-4}$\\
+	\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
+
+\subsection{Classification and Regression Fitting}
+The process and training parameters for both classification and regression are very similar.
+We build a model with either a classifer or regression head and the appropriate output and initialize those head weights randomly.
+We load the LM weights for the layers below and then train the head first before unfreezing the rest of the layers and training further.
+We used differential learning rates as explained in \cite{HowarRuder:DBLP:journals/corr/abs-1801-06146} for the layers so as not to lose the pre-training already done.
+
+With the same learning rate and weight decay we apply a 5-fold cross-validation on the outputs and take the mean across the folds.
+We sample 20 random seeds \ref{sec:rand_seeds} to find the best init for our gradient descent search and select the best validation F1 metric or MSE for use in our test submission.
+\subsubsection{Classifier setup}  For the classifier, we have a softmax head and label smoothing loss.
+We oversample the minority class to 50\% 0 and 1 for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
+\subsubsection{Regression setup}  For the regression, we fill all N/A labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
+
+\begin{table}[ht]
+	% table caption is above the table
+	\caption{Classificaiton and Regression Training Parameters}
+	\label{tab:clas_training}       % Give a unique label
+	\begin{tabular}{ll}
+		\hline\noalign{\smallskip}
+		Param & Value \\
+		\noalign{\smallskip}\hline\noalign{\smallskip}
+		Weight Decay & 0.1  \\
+		Dropout Mult &  0.7 \\
+		Learning Rate (Head)& 2 epochs at $1*10^{-2}$\\
+		Cont. Training & 15 epochs with diff lr:($1*10^{-3}/(2.6^4)$, $5*10^{-3}$)\\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+\end{table}
 
 \subsection{Random Seed as a Hyperparamter}
+\label{sec:rand_seeds}
+The random seed sets the initial random weights of the head layer.
+This initialization determines where on the optimization surface you start your gradient descent and effects the final F1 metric you can achieve with your model.
+Across each of the 20 random seeds, we average the 5-folds and get a single F1 metric on the validation set.
+The histogram of outcomes is shown in \ref{fig1} and covers a range  from 0.820 to 0.825 in the validation set.
+We selected our single best random seed for the test submission.
+With more exploration, a better seed could likely be found.
+We only tried a single seed for the LM training but one could do a similar search with random seeds there and select the best down-stream seed similar to \cite{poleval}
+
+\begin{figure}[h]
+	% Use the relevant command to insert your figure file.
+	% For example, with the graphicx package use
+	\includegraphics[width=0.75\textwidth]{seed_hist_f1}
+	\caption{Histogram of F1 metric averaged across 5-fold metric}
+	\label{fig:random_seed_hist}
+\end{figure}
 
@@
 
-\section*{Acknowlegements}
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
-%
-% For two-column wide figures use
-\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
-%
-% For tables use
-\begin{table}
-% table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-\begin{tabular}{llll}
-\hline\noalign{\smallskip}
-first & second & third & fourth \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
-
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
+\begin{acknowledgements}
+If you'd like to thank anyone, place your comments here
+and remove the percent signs.
+\end{acknowledgements}
 

### 2019-06-12 prod/paper/paper_draft.tex
another paper revision

@@
 \begin{abstract}
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
+
+All the code for this project is included in a GitHub \cite{} repository for easy reference.
+Some details are omitted below for clarity but can be found in the notebooks, code and execution instructions.
+
 \keywords{First keyword \and Second keyword \and More}
@@
 \label{sec:task}
-The \textit{Humor Analysis based on Humor Annotation (HAHA)} competition asked for analysis of two tasks in the Spanish language based on a coprpus of publicly collected data ~\cite{castro2018crowd}:
+The \textit{Humor Analysis based on Humor Annotation (HAHA)} competition asked for analysis of two tasks in the Spanish language based on a corpus of publicly collected data ~\cite{castro2018crowd}:
 \begin{itemize}
@@
 \end{itemize}
-HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons) and a True/False labels as well as a ``Funninness Score'' that is the average of the 1 to 5 start votes cast.
+The HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons), a binary humor label, the number of votes for each of five star ratings and a ``Funninness Score'' that is the average of the 1 to 5 star votes cast.
 Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/}.
@@
 \label{sec:system}
-We generally follow the method of ULMFiT ~\cite{DBLP:journals/corr/abs-1801-06146}
+We generally follow the method of ULMFiT ~\cite{HowardRuder:DBLP:journals/corr/abs-1801-06146} including pre-training and differential learning rates. 
 \begin{enumerate}
@@
 For our initial training, we  collected 475,143 tweets in the Spanish language using tweepy ~\cite{Tweepy}.
-The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is used to train.
+The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that often used to train an LM.
 
-We combined the labeled and un-labeled text data so that we have the largest corpus of language for our fine-tuning step. 
+For the fine-tuning step, we combined the labeled and un-labeled text data for the LM training.
 \subsection{Cleaning}
@@
 \end{itemize} 
-\pagebreak  %move as needed to keep tweet text together
+%\pagebreak  %move as needed to keep tweet text together
 The following example shows the application of this data cleaning to a single tweet:
@@
 \label{sec:4}
-
 \subsection{LM Training and Fine-tuning}
-With our data cleaned and tokenized we move to training the LM using a 90/10 training/validation split.
-For the LM, we selected a AWD\_LSTM \cite{} model included in Fastai with QRNN units, 2304 hidden-states, 3 layers and a softmax layer on the end to predict the next-word.
+We train the LM using a 90/10 training/validation split and report the validation loss and accuracy of next-word prediction on the validation set.
+For the LM, we selected a AWD\_LSTM \cite{merity?} model included in Fastai with QRNN units, 2304 hidden-states, 3 layers and a softmax layer on the end to predict the next-word.
 We tied the embedding weights on the encoder and decoder for training.
@@
 
-Both the LM and the Classifer models used label smoothing \cite{labelsmooth} of the flattened cross-entropy loss.
-With the classifier, this allowed us to train without gradual unfreezing of the layers as discussed in \cite{HowarRuder:DBLP:journals/corr/abs-1801-06146}
-Parameters used for training all networks can be found in \ref{tab:tab_training}.
+Our loss is label smoothing\cite{labelsmooth} of the flattened cross-entropy loss. 
+Parameters used for training and finetuning are shown in Table \ref{tab:tab_training}.
 For all the networks we applied a dropout multiplier that scales the dropout used throughout the network.  We used the Adam optimizer with weight decay as indicated in the table.
@@
 Following the work of \cite{smith}  we found the largest learning-rate that we could apply and then ran a one-cycle policy \cite{} for a single epoch.
-We then ran subsequent training with lower learning rates, again indicated in \ref{tab:tab_training}.
+We then ran subsequent training with lower learning rates, again indicated in Table \ref{tab:tab_training}.
 
@@
 \subsection{Classification and Regression Fitting}
-The process and training parameters for both classification and regression are very similar.
-We build a model with either a classifer or regression head and the appropriate output and initialize those head weights randomly.
-We load the LM weights for the layers below and then train the head first before unfreezing the rest of the layers and training further.
-We used differential learning rates as explained in \cite{HowarRuder:DBLP:journals/corr/abs-1801-06146} for the layers so as not to lose the pre-training already done.
+Again, following the playbook from \cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change out the head of the network to a softmax or linear output layer and then load the LM weights for the layers below.
+We train just the new head from the random init, then unfreeze the entire network and train with differential learning rats.
+With the classifier, we again used label smoothing which allows us to train without gradual unfreezing.
 
-With the same learning rate and weight decay we apply a 5-fold cross-validation on the outputs and take the mean across the folds.
-We sample 20 random seeds \ref{sec:rand_seeds} to find the best init for our gradient descent search and select the best validation F1 metric or MSE for use in our test submission.
+With the same learning rate and weight decay we apply a 5-fold cross-validation on the outputs and take the mean across the folds as our ensemble.
+We sample 20 random seeds (see more in sec \ref{sec:rand_seeds}) to find the best initialization for our gradient descent search.
+From these samples, we select the best validation F1 metric or MSE for use in our test submission.
 \subsubsection{Classifier setup}  For the classifier, we have a softmax head and label smoothing loss.
-We oversample the minority class to 50\% 0 and 1 for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
+We oversample the minority class balance the outcomes for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
 \subsubsection{Regression setup}  For the regression, we fill all N/A labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
@@
 \label{sec:rand_seeds}
-The random seed sets the initial random weights of the head layer.
-This initialization determines where on the optimization surface you start your gradient descent and effects the final F1 metric you can achieve with your model.
+For classification and regression, the random seed sets the initial random weights of the head layer. This initialization effects the final F1 metric you can achieve with your model.
+
 Across each of the 20 random seeds, we average the 5-folds and get a single F1 metric on the validation set.
-The histogram of outcomes is shown in \ref{fig1} and covers a range  from 0.820 to 0.825 in the validation set.
+The histogram of outcomes is shown in Figure \ref{fig:random_seed_hist} and covers a range  from 0.820 to 0.825 in the validation set.
 We selected our single best random seed for the test submission.

### 2019-06-13 prod/paper/paper_draft.tex
added citations

@@
 \label{intro}
-Included citations as necessary: ~\cite{Nobody06}
+
 \paragraph{Contribution} Our contribution with this work is..
@@
 \label{sec:task}
-The \textit{Humor Analysis based on Humor Annotation (HAHA)} competition asked for analysis of two tasks in the Spanish language based on a corpus of publicly collected data ~\cite{castro2018crowd}:
+The \textit{Humor Analysis based on Humor Annotation (HAHA) 2019}\cite{overview_haha2019} competition asked for analysis of two tasks in the Spanish language based on a corpus of publicly collected data ~\cite{castro2018crowd}:
 \begin{itemize}
@@
 We train the LM using a 90/10 training/validation split and report the validation loss and accuracy of next-word prediction on the validation set.
-For the LM, we selected a AWD\_LSTM \cite{merity?} model included in Fastai with QRNN units, 2304 hidden-states, 3 layers and a softmax layer on the end to predict the next-word.
+For the LM, we selected a AWD\_LSTM \cite{Merity:DBLP:journals/corr/abs-1708-02182} model included in Fastai with QRNN\cite{Bradbury:DBLP:journals/corr/BradburyMXS16} units, 2304 hidden-states, 3 layers and a softmax layer on the end to predict the next-word.
 We tied the embedding weights on the encoder and decoder for training.
@@
 
-Our loss is label smoothing\cite{labelsmooth} of the flattened cross-entropy loss. 
+Our loss is label smoothing\cite{Labelsmoothing:DBLP:journals/corr/PereyraTCKH17} of the flattened cross-entropy loss. 
 Parameters used for training and finetuning are shown in Table \ref{tab:tab_training}.
@@
 
-Following the work of \cite{smith}  we found the largest learning-rate that we could apply and then ran a one-cycle policy \cite{} for a single epoch.
+Following the work of \cite{Smith:DBLP:journals/corr/abs-1803-09820}  we found the largest learning-rate that we could apply and then ran a one-cycle policy \cite{} for a single epoch.
 We then ran subsequent training with lower learning rates, again indicated in Table \ref{tab:tab_training}.
@@
 We oversample the minority class balance the outcomes for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
-\subsubsection{Regression setup}  For the regression, we fill all N/A labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
+\subsubsection{Regression setup}  For the regression, we fill all \verb|#N/A| labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
 
@@
 % BibTeX users please use one of
-\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{fullname}      % basic style, author-year citations
+
+%\bibliographystyle{spbasic}      % basic style, author-year citations
+\bibliographystyle{spmpsci}      % mathematics and physical sciences
 %\bibliographystyle{spphys}       % APS-like style for physics

### 2019-06-14 prod/paper/paper_draft.tex
draft without intro, abstract, conclusion

@@
 %\documentclass{svjour3}                     % onecolumn (standard format)
-\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
 %\documentclass[twocolumn]{svjour3}          % twocolumn
@@
 
-All the code for this project is included in a GitHub \cite{} repository for easy reference.
+All the code for this project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference.
 Some details are omitted below for clarity but can be found in the notebooks, code and execution instructions.
@@
 For our initial training, we  collected 475,143 tweets in the Spanish language using tweepy ~\cite{Tweepy}.
-The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that often used to train an LM.
+The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is often used to train an LM.
 
-For the fine-tuning step, we combined the labeled and un-labeled text data for the LM training.
+In the fine-tuning step, we combined the labeled and un-labeled text data for the LM training.
 \subsection{Cleaning}
-We applied a list of default cleanup functions included in Fastai and added an additional one for this Twitter dataset.
+We applied a list of default cleanup functions included in Fastai\cite{} and added an additional one for this Twitter dataset.
 \begin{itemize}
@@
 
-Following the work of \cite{Smith:DBLP:journals/corr/abs-1803-09820}  we found the largest learning-rate that we could apply and then ran a one-cycle policy \cite{} for a single epoch.
-We then ran subsequent training with lower learning rates, again indicated in Table \ref{tab:tab_training}.
+Following the work of Smith\cite{Smith:DBLP:journals/corr/abs-1803-09820}  we found the largest learning-rate that we could apply and then ran a one-cycle policy for a single epoch.
+We then ran subsequent training with one-cycle and lower learning rates indicated in Table \ref{tab:tab_training}.
 
@@
 \subsection{Classification and Regression Fitting}
-Again, following the playbook from \cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change out the head of the network to a softmax or linear output layer and then load the LM weights for the layers below.
-We train just the new head from the random init, then unfreeze the entire network and train with differential learning rats.
-With the classifier, we again used label smoothing which allows us to train without gradual unfreezing.
+Again, following the play-book from \cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change out the head of the network to a softmax or linear output layer and then load the LM weights for the layers below.
+We train just the new head from the random initialization, then unfreeze the entire network and train with differential learning rates.
 
 With the same learning rate and weight decay we apply a 5-fold cross-validation on the outputs and take the mean across the folds as our ensemble.
-We sample 20 random seeds (see more in sec \ref{sec:rand_seeds}) to find the best initialization for our gradient descent search.
+We sample 20 random seeds (see more in section \ref{sec:rand_seeds}) to find the best initialization for our gradient descent search.
 From these samples, we select the best validation F1 metric or MSE for use in our test submission.
-\subsubsection{Classifier setup}  For the classifier, we have a softmax head and label smoothing loss.
-We oversample the minority class balance the outcomes for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
+\subsubsection{Classifier setup}  For the classifier, we have a softmax head and label smoothing loss which allows us to train without gradual unfreezing.
+We oversample the minority class to balance the outcomes for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
 \subsubsection{Regression setup}  For the regression, we fill all \verb|#N/A| labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
@@
 Across each of the 20 random seeds, we average the 5-folds and get a single F1 metric on the validation set.
-The histogram of outcomes is shown in Figure \ref{fig:random_seed_hist} and covers a range  from 0.820 to 0.825 in the validation set.
+The histogram of 20-seed outcomes is shown in Figure \ref{fig:random_seed_hist} and covers a range  from 0.820 to 0.825 in the validation set.
 We selected our single best random seed for the test submission.

### 2019-06-14 prod/paper/paper_draft.tex
first draft of paper

@@
 }
-\subtitle{Do you have a subtitle?\\ If so, write it here}
+%\subtitle{Do you have a subtitle?\\ If so, write it here}
 
-\titlerunning{Short form of title}        % if too long for running head
+%\titlerunning{Short form of title}        % if too long for running head
 
@@
 
-\authorrunning{Short form of author list} % if too long for running head
-
+%\authorrunning{Short form of author list} % if too long for running head
+\institute{}
 %\institute{F. Author \at
@@
 \begin{abstract}
-
-All the code for this project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference.
-Some details are omitted below for clarity but can be found in the notebooks, code and execution instructions.
+Our entry into the \textit{HAHA 2019 Challenge} came in $3^{rd}$ in the classification task and $2^{nd}$ in the regression task.
+We describe our system and innovations and compare our results to a Naive Bayes classifier.
+All the code for ourproject is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference and replication by others.
 
@@
 \label{intro}
+\newcommand{\chapquote}[3]{\begin{quotation} \textit{#1} \end{quotation} \begin{flushright} - #2, \textit{#3}\end{flushright} }
 
-\paragraph{Contribution} Our contribution with this work is..
+\begin{quote}
+- !`Socorro, me ha picado una víbora!\\
+- ?`Cobra?\\
+- No, gratis.\footnote{https://www.fluentin3months.com/spanish-jokes/}
+\end{quote}
+Google Translation:
+\begin{quote}
+- Help, I was bitten by a snake!\\
+- Does it charge?\\
+- Not free.
+\end{quote}
+Humor does not translate well because it often relies on double-meaning or a subtle play on the words or context.
+Thus, one would imagine building a system to classify the humor of tweets would be difficult.
+However, with transfer-learning and the Fastai libray\footnote{https://docs.fast.ai/}, you can quickly get a high quality classifier working in a language you don't even speak which will easily out-pace a Naive Bayes SVM baseline \footnote{https://twitter.com/radamihalcea/status/1119020144389443585}
+
+Rather than hand-crafted language features, we have taken an "end to end" approach building from the raw text to a final model that achieve the tasks as presented.
+Our paper lays out the details of the system and our code can be found in a GitHub repo for use by other researchers to extend the state of the art in sentiment analysis.
+
+\paragraph{Contribution} Our key contributions are three fold.
+First, we apply transfer-learning of a lanugage model based on a larger corpus of tweets.
+Second, we use a label smoothed loss to allow full training of the final model without gradual unfreezing.
+Third, we select the best classifier or regression model based on cross-validation and 20 random-seed initialization in the final network training step.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 	% Use the relevant command to insert your figure file.
@@
 
+\subsection{Results}
+Below in Table \ref{tab:tab_results} we layout three results from our submissions in the competition.
+The first is the Naive Bays SVM solution showing an F1 of 0.7548.
+Second is our first random seed selected for the classifier which produces a 0.8083 result.
+While better than the NBSVM solution, we can do better by picking the best F1 from the 20 seeds that we selected.
+That result is in the final row and gets our final submission value of 0.8099.
+Note that in our validation set achieved an F1 of 0.8254 but this is somewhat overfit from the many trials we have run and our final test set is a drop of 0.0155
+
+\begin{table}[ht]
+	% table caption is above the table
+	\caption{Comparative Results}
+	\label{tab:tab_results}
+	\begin{tabular}{lllll}
+		\hline\noalign{\smallskip}
+		 & Accuracy & Precision & Recall & F1 \\
+		\noalign{\smallskip}\hline\noalign{\smallskip}
+NBSVM &      0.8223 & 0.8180 & 0.7007 & 0.7548 \\
+First Seed & 0.8461 & 0.7869 & 0.8309 & 0.8083 \\
+Best Seed &  0.8458 & 0.7806 & 0.8416 & \textbf{0.8099} \\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+\end{table}
+
 \section{Conclusion}
 \label{sec:5}
+This paper describes our implementation of a neural net model for classification and regression in the HAHA 2019 challenge.
+Our solution placed third in Task 1 and second in task 2 in the final standings.
+We describe the data collection, pre-training and final model building steps.
+Additionally, we have open-sourced all the code used in this contest so it can be easily duplicate to further research in this task in the future.
 

### 2019-06-15 prod/paper/paper_draft.tex
with Kyle first edits

@@
 \begin{abstract}
-Our entry into the \textit{HAHA 2019 Challenge} came in $3^{rd}$ in the classification task and $2^{nd}$ in the regression task.
-We describe our system and innovations and compare our results to a Naive Bayes classifier.
-All the code for ourproject is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference and replication by others.
+Our entry into the \textit{HAHA 2019 Challenge} placed $3^{rd}$ in the classification task and $2^{nd}$ in the regression task.
+We describe our system and innovations, as well as comparing our results to a Naive Bayes baseline.
+All the code for our project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference and to enable replication by others.
 
@@
 \end{quote}
-Humor does not translate well because it often relies on double-meaning or a subtle play on the words or context.
-Thus, one would imagine building a system to classify the humor of tweets would be difficult.
-However, with transfer-learning and the Fastai libray\footnote{https://docs.fast.ai/}, you can quickly get a high quality classifier working in a language you don't even speak which will easily out-pace a Naive Bayes SVM baseline \footnote{https://twitter.com/radamihalcea/status/1119020144389443585}
+Humor does not translate well because it often relies on double-meaning or a subtle play on word choice, pronunciation, or context.
+These issues are further exacerbated in areas where space is a premium (as frequent on social media platforms), often leading to usage and development of shorthand, in-jokes, and self-reference.
+Thus, building a system to classify the humor of tweets is a difficult task.
+However, with transfer-learning and the Fastai library\footnote{https://docs.fast.ai/}, we show the power of these tools in order to build a high quality classifier in a foreign language.
+Our system strongly outperforms a Naive Bayes SVM baseline, which is frequently considered a "strong baseline" for many NLP related tasks \footnote{https://twitter.com/radamihalcea/status/1119020144389443585}.
 
@@
 \paragraph{Contribution} Our key contributions are three fold.
-First, we apply transfer-learning of a lanugage model based on a larger corpus of tweets.
+First, we apply transfer-learning of a language model based on a larger corpus of tweets.
 Second, we use a label smoothed loss to allow full training of the final model without gradual unfreezing.
-Third, we select the best classifier or regression model based on cross-validation and 20 random-seed initialization in the final network training step.
+Third, we select the best model for each task based on cross-validation and 20 random-seed initialization in the final network training step.
 
@@
 \begin{itemize}
-\item \textbf{Task1: Humor Detection}:Detemine if a tweet is humorous. System ranking is based on F1 score which will balance precision and accuracy.
-\item \textbf{Task2: Funniness Score}:If humorous, what is the average humor rating of the tweet. System ranking is based on RMSE.
+\item \textbf{Task1: Humor Detection}:Determine if a tweet is humorous. System ranking is based on F1 score which balances precision and accuracy.
+\item \textbf{Task2: Funniness Score}:If humorous, what is the average humor rating of the tweet? System ranking is based on RMSE.
 \end{itemize}
-The HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons), a binary humor label, the number of votes for each of five star ratings and a ``Funninness Score'' that is the average of the 1 to 5 star votes cast.
+The HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons), a binary humor label, the number of votes for each of five star ratings and a ``Funniness Score'' that is the average of the 1 to 5 star votes cast.
 Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/}.
@@
 	\item Replace repetition at the character level (ie. \verb|grrrreat| becomes \verb|g xxrep r 3 eat|)
-	\item Replace repition at the word level (similar to above)
+	\item Replace repetition at the word level (similar to above)
 	\item Deal with ALL CAPS words replacing with a token and converting to lower case.
@@
 \subsection{LM Training and Fine-tuning}
-We train the LM using a 90/10 training/validation split and report the validation loss and accuracy of next-word prediction on the validation set.
-For the LM, we selected a AWD\_LSTM \cite{Merity:DBLP:journals/corr/abs-1708-02182} model included in Fastai with QRNN\cite{Bradbury:DBLP:journals/corr/BradburyMXS16} units, 2304 hidden-states, 3 layers and a softmax layer on the end to predict the next-word.
+We train the LM using a 90/10 training/validation split, reporting the validation loss and accuracy of next-word prediction on the validation set.
+For the LM, we selected a AWD\_LSTM \cite{Merity:DBLP:journals/corr/abs-1708-02182} model included in Fastai with QRNN\cite{Bradbury:DBLP:journals/corr/BradburyMXS16} units, 2304 hidden-states, 3 layers and a softmax layer to predict the next-word.
 We tied the embedding weights on the encoder and decoder for training.
-We performed some simple tests with LSTM units and with a Transformer Language model and found all the models were similar in performance during LM training.
-We chose the QRNN units to speed up training.
-The model has about 60 million trainable parameters.
+We performed some simple tests with LSTM units and a Transformer Language model, finding all models were similar in performance during LM training.
+We thus chose to use QRNN units due to improved training speed compared to the alternatives.
+This model has about 60 million trainable parameters.
 
@@
 Parameters used for training and finetuning are shown in Table \ref{tab:tab_training}.
-For all the networks we applied a dropout multiplier that scales the dropout used throughout the network.  We used the Adam optimizer with weight decay as indicated in the table.
+For all networks we applied a dropout multiplier which scales the dropout used throughout the network.  We used the Adam optimizer with weight decay as indicated in the table.
 
@@
 \subsection{Classification and Regression Fitting}
-Again, following the play-book from \cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change out the head of the network to a softmax or linear output layer and then load the LM weights for the layers below.
-We train just the new head from the random initialization, then unfreeze the entire network and train with differential learning rates.
+Again, following the play-book from \cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change pre-trained network head to a softmax or linear output layer (as appropriate for the transfer task) and then load the LM weights for the layers below.
+We train just the new head from random initialization, then unfreeze the entire network and train with differential learning rates.
 
@@
 We oversample the minority class to balance the outcomes for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
-\subsubsection{Regression setup}  For the regression, we fill all \verb|#N/A| labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
+\subsubsection{Regression setup}  For the regression task, we fill all \verb|#N/A| labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
 
@@
 	% table caption is above the table
-	\caption{Classificaiton and Regression Training Parameters}
+	\caption{Classification and Regression Training Parameters}
 	\label{tab:clas_training}       % Give a unique label
@@
 \label{sec:rand_seeds}
-For classification and regression, the random seed sets the initial random weights of the head layer. This initialization effects the final F1 metric you can achieve with your model.
+For classification and regression, the random seed sets the initial random weights of the head layer. This initialization affects the final F1 metric achievable.
 
-Across each of the 20 random seeds, we average the 5-folds and get a single F1 metric on the validation set.
-The histogram of 20-seed outcomes is shown in Figure \ref{fig:random_seed_hist} and covers a range  from 0.820 to 0.825 in the validation set.
+Across each of the 20 random seeds, we average the 5-folds and obtain a single F1 metric on the validation set.
+The histogram of 20-seed outcomes is shown in Figure \ref{fig:random_seed_hist} and covers a range  from 0.820 to 0.825 over the validation set.
 We selected our single best random seed for the test submission.
 With more exploration, a better seed could likely be found.
-We only tried a single seed for the LM training but one could do a similar search with random seeds there and select the best down-stream seed similar to \cite{poleval}
+Though we only use a single seed for the LM training, one could do a similar search with random seeds for LM pretraining, and further select the best down-stream seed similar to \cite{poleval}
 
@@
 Below in Table \ref{tab:tab_results} we layout three results from our submissions in the competition.
-The first is the Naive Bays SVM solution showing an F1 of 0.7548.
+The first is the baseline Naive Bayes SVM solution, with an F1 of 0.7548.
 Second is our first random seed selected for the classifier which produces a 0.8083 result.
-While better than the NBSVM solution, we can do better by picking the best F1 from the 20 seeds that we selected.
-That result is in the final row and gets our final submission value of 0.8099.
-Note that in our validation set achieved an F1 of 0.8254 but this is somewhat overfit from the many trials we have run and our final test set is a drop of 0.0155
+While better than the NB-SVM solution, we can do better by picking the best F1 from the 20 seeds that we selected.
+That result is in the final row and resulting in our final submission value of 0.8099.
+Note that applying this model over our validation set achieved an F1 of 0.8254 however our final test set is slightly lower, a drop of 0.0155 to the final test F1 of 0.8099.
 
@@
 This paper describes our implementation of a neural net model for classification and regression in the HAHA 2019 challenge.
-Our solution placed third in Task 1 and second in task 2 in the final standings.
-We describe the data collection, pre-training and final model building steps.
-Additionally, we have open-sourced all the code used in this contest so it can be easily duplicate to further research in this task in the future.
+Our solution placed third in Task 1 and second in task 2 in the final competition standings.
+We describe the data collection, pre-training, and final model building steps for this contest.
+Additionally, we have open-sourced all  code used in this contest to further enable research on this task in the future.
 

### 2019-06-15 prod/paper/paper_draft.tex
adding more detail to Abstract and Conclusion

@@
 
-%\titlerunning{Short form of title}        % if too long for running head
+\titlerunning{Short form of title}        % if too long for running head
 
@@
 
-%\authorrunning{Short form of author list} % if too long for running head
+\authorrunning{Farzin 2019} % if too long for running head
 \institute{}
@@
 We describe our system and innovations, as well as comparing our results to a Naive Bayes baseline.
+We found that a large Twitter based corpus allowed us to train a language model from scratch that is focused on Spanish Twitter.
+With transfer learning, we moved this embedded information into our competition model and better predict tweets we have never seen but that are consistent with those in Spanish Twitter.
+Finally, manually collected labels for the competition inherently have errors.
+To overcome this we applied label smoothing to our loss and reduce the confidence in our model for either label in the classification task.
 All the code for our project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference and to enable replication by others.
@@
 \subsection{Additional Data}
-For our initial training, we  collected 475,143 tweets in the Spanish language using tweepy ~\cite{Tweepy}.
+We collected a corpus for our LM based on Spanish Twitter using tweepy~\cite{Tweepy} run for three 4 hours sessions and collecting any tweet with the terms 'el','su','lo','y' or 'en'.
+We excluded retweets to minimize repeated examples in our language model training.
+In total, we collected 475,143 tweets.
+This data set is nearly 16 times larger than the text provided by the competition.
 The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is often used to train an LM.
 
-In the fine-tuning step, we combined the labeled and un-labeled text data for the LM training.
+In the fine-tuning step, we combined the train and test text data \textit{without labels} from the contest data.
 \subsection{Cleaning}
@@
 For the LM, we selected a AWD\_LSTM \cite{Merity:DBLP:journals/corr/abs-1708-02182} model included in Fastai with QRNN\cite{Bradbury:DBLP:journals/corr/BradburyMXS16} units, 2304 hidden-states, 3 layers and a softmax layer to predict the next-word.
-We tied the embedding weights on the encoder and decoder for training.
+We tied the embedding weights\cite{WeightTie:DBLP:journals/corr/PressW16} on the encoder and decoder for training.
 We performed some simple tests with LSTM units and a Transformer Language model, finding all models were similar in performance during LM training.
@@
 This paper describes our implementation of a neural net model for classification and regression in the HAHA 2019 challenge.
-Our solution placed third in Task 1 and second in task 2 in the final competition standings.
+Our solution placed third in Task 1 and second in Task 2 in the final competition standings.
 We describe the data collection, pre-training, and final model building steps for this contest.
+Twitter has slang and abbreviations that are unique to the short-format as well as generous use of emoticons.
+To capture these features, we collected our own dataset based on Spanish Tweets that is 16 times larger than the competition data set and allowed us to pre-train a langauge model.
+Humor is subtle and using a label smoothed loss allowed us to not become too overconfident in our predictions and train more quickly without the gradual unfreezing required by ULMFiT.
 Additionally, we have open-sourced all  code used in this contest to further enable research on this task in the future.
 
+\section{other}
+
+%%  Comment from Kyle:
+%%Maybe you have some good advice to give other people related to points one and two of your main contributions, what do you think the primary benefit of transfer learning was - especially the use of tweets for the vocab and so on, versus the "standard" wikipedia?
+%
+%Pretraining allows the model to get "close" to the right language model
+%Pre-training uses a wider universe of language than just the model training set.  We have a better chance to predict the test-set data by leveraging additional data.
+%
+%%As for the label smoothing, what is your general insight on what settings of label smoothing worked well, why penalizing confident stuff was extra useful here?	
+%%	For example in 4.2.1, why does label smoothing bypass gradual unfreezing? 
+%
+%With so many trainable params models can become focused on refining the prediiction on already correct predictions (going from .85 to .95 in the softmax output).
+Gradual unfreezing prevents this kind of over-fitting by regularizing through restricting the params that can be fit.
+Label smoothing achieves the same thing by preventing the maximum classification from becoming too large.
+%
+%Manually built labels always lead to some errors.
+there could be some that are only marginally funny, yet classified as "Humorous."  We don't want to be overconfident in our classification of these jokes,
+%and label smoothing helps us to overcome that noise. 
+%
+%
+%Twitter has slang and abbreviations that are unique to the short-format as well as generous use of emoticons.
+
 \begin{acknowledgements}
-If you'd like to thank anyone, place your comments here
-and remove the percent signs.
+The author would like to thank Kyle Kastner for his edits, suggestions and recommendations in writing up these results. 
 \end{acknowledgements}

### 2019-06-16 prod/paper/paper_draft.tex
another revision

@@
 
-\title{Insert your title here%\thanks{Grants or other notes
+\title{ULMFiT for Joke Classification in Spanish%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 
-\titlerunning{Short form of title}        % if too long for running head
+\titlerunning{}        % if too long for running head
 
-\author {\textbf{Bobak Farzin$^1$}, \textbf{Nombre Apellidos2$^2$}\\
+\author {\textbf{Bobak Farzin$^1$}\\
 	$^1$bfarzin@gmail.com\\
-	$^2$Universidad o lugar de trabajo\\
 }
@@
 
-\date{Received: 15 June 2019 / Accepted: date}
+\date{Received: 17 June 2019 / Accepted: date}
 % The correct dates will be entered by the editor
@@
 We describe our system and innovations, as well as comparing our results to a Naive Bayes baseline.
-We found that a large Twitter based corpus allowed us to train a language model from scratch that is focused on Spanish Twitter.
-With transfer learning, we moved this embedded information into our competition model and better predict tweets we have never seen but that are consistent with those in Spanish Twitter.
-Finally, manually collected labels for the competition inherently have errors.
-To overcome this we applied label smoothing to our loss and reduce the confidence in our model for either label in the classification task.
+A large Twitter based corpus allowed us to train a language model from scratch focused on Spanish and transfer that knowledge to our competition model.
+To overcome the inherent errors in some labels we reduce our class confidence with label smoothing in the loss function.
 All the code for our project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference and to enable replication by others.
@@
 Thus, building a system to classify the humor of tweets is a difficult task.
-However, with transfer-learning and the Fastai library\footnote{https://docs.fast.ai/}, we show the power of these tools in order to build a high quality classifier in a foreign language.
-Our system strongly outperforms a Naive Bayes SVM baseline, which is frequently considered a "strong baseline" for many NLP related tasks \footnote{https://twitter.com/radamihalcea/status/1119020144389443585}.
+However, with transfer-learning and the Fastai library\footnote{https://docs.fast.ai/}, we can build a high quality classifier in a foreign language.
+Our system outperforms a Naive Bayes SVM baseline, which is frequently considered a "strong baseline" for many NLP related tasks \footnote{https://twitter.com/radamihalcea/status/1119020144389443585}.
 
-Rather than hand-crafted language features, we have taken an "end to end" approach building from the raw text to a final model that achieve the tasks as presented.
+Rather than hand-crafted language features, we have taken an "end to end" approach building from the raw text to a final model that achieves the tasks as presented.
 Our paper lays out the details of the system and our code can be found in a GitHub repo for use by other researchers to extend the state of the art in sentiment analysis.
 
-\paragraph{Contribution} Our key contributions are three fold.
+\paragraph{Contribution} Our contributions are three fold.
 First, we apply transfer-learning of a language model based on a larger corpus of tweets.
-Second, we use a label smoothed loss to allow full training of the final model without gradual unfreezing.
+Second, we use a label smoothed loss, which provides regularization and allows full training of the final model without gradual unfreezing.
 Third, we select the best model for each task based on cross-validation and 20 random-seed initialization in the final network training step.
@@
 In total, we collected 475,143 tweets.
-This data set is nearly 16 times larger than the text provided by the competition.
-The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is often used to train an LM.
+This data set is nearly 16 times larger than the text provided by the competition alone.
+The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is often used to train an LM from scratch.
 
@@
 \subsection{Cleaning}
-We applied a list of default cleanup functions included in Fastai\cite{} and added an additional one for this Twitter dataset.
+We applied a list of default cleanup functions included in Fastat and added an additional one for this Twitter dataset.
 \begin{itemize}
@@
 
-Our loss is label smoothing\cite{Labelsmoothing:DBLP:journals/corr/PereyraTCKH17} of the flattened cross-entropy loss. 
 Parameters used for training and finetuning are shown in Table \ref{tab:tab_training}.
@@
 From these samples, we select the best validation F1 metric or MSE for use in our test submission.
-\subsubsection{Classifier setup}  For the classifier, we have a softmax head and label smoothing loss which allows us to train without gradual unfreezing.
-We oversample the minority class to balance the outcomes for better training using SMOTE \cite{Chawla:2002:SSM:1622407.1622416}.
-\subsubsection{Regression setup}  For the regression task, we fill all \verb|#N/A| labels with scores of 0.  We add a linear head output and mean-squared-error (MSE) loss function.
+\subsubsection{Classifier setup}  For the classifier, we have a hidden layer and softmax head.
+We over-sample the minority class to balance the outcomes for better training using SMOTE\cite{Chawla:2002:SSM:1622407.1622416}.
+Our loss is label smoothing\cite{Labelsmoothing:DBLP:journals/corr/PereyraTCKH17} of the flattened cross-entropy loss.
+Gradual unfreezing allows us to avoid catastropic forgetting, focus each stage of training and preventing over-fitting of the parameters to the training cases.
+We take an alternative approach to regularization and in our experiments found that we got similar results with label smoothing but without the separate steps and learning rate refinement required of gradual unfreezing.
+\subsubsection{Regression setup}  For the regression task, we fill all \verb|#N/A| labels with scores of 0.  We add a hidden layer and linear output head and mean-squared-error (MSE) loss function.
 
@@
 With more exploration, a better seed could likely be found.
-Though we only use a single seed for the LM training, one could do a similar search with random seeds for LM pretraining, and further select the best down-stream seed similar to \cite{poleval}
+Though we only use a single seed for the LM training, one could do a similar search with random seeds for LM pre-training, and further select the best down-stream seed similar to \cite{Poleval:DBLP:journals/corr/abs-1810-10222}
 
@@
 Second is our first random seed selected for the classifier which produces a 0.8083 result.
-While better than the NB-SVM solution, we can do better by picking the best F1 from the 20 seeds that we selected.
-That result is in the final row and resulting in our final submission value of 0.8099.
-Note that applying this model over our validation set achieved an F1 of 0.8254 however our final test set is slightly lower, a drop of 0.0155 to the final test F1 of 0.8099.
+While better than the NB-SVM solution, we pick the best validation F1 from the 20 seeds we tried.
+This produced our final submission of 0.8099.
+Note that applying this model over our validation set achieved an F1 of 0.8254 and a test set F1 of 0.8099 - a drop of 0.0155 in F1 for the true out-of-sample data.
 
@@
 This paper describes our implementation of a neural net model for classification and regression in the HAHA 2019 challenge.
-Our solution placed third in Task 1 and second in Task 2 in the final competition standings.
+Our solution placed $3^{rd}$ in Task 1 and $2^{nd}$ in Task 2 in the final competition standings.
 We describe the data collection, pre-training, and final model building steps for this contest.
@@
 Humor is subtle and using a label smoothed loss allowed us to not become too overconfident in our predictions and train more quickly without the gradual unfreezing required by ULMFiT.
-Additionally, we have open-sourced all  code used in this contest to further enable research on this task in the future.
+We have open-sourced all  code used in this contest to further enable research on this task in the future.
 

### 2019-06-17 prod/paper/newformat/paper_draft.tex
with new format

--- 2019-06-16 prod/paper/paper_draft.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
 %
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-
-%
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
+\documentclass[runningheads]{llncs}
 %
 \usepackage{graphicx}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
 %
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
+
 \begin{document}
 
-\title{ULMFiT for Joke Classification in Spanish%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
-}
+\title{ULMFiT for Joke Classification in Spanish}
+
+\author{Bobak Farzin\inst{1}}
+%
+\authorrunning{Farzin 2019}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{	\email{bfarzin@gmail.com}}
+
 %\subtitle{Do you have a subtitle?\\ If so, write it here}
-
-\titlerunning{}        % if too long for running head
-
-\author {\textbf{Bobak Farzin$^1$}\\
-	$^1$bfarzin@gmail.com\\
-}
-
-%\author{Bobak Farzin         \and
-%        Second Author %etc.
-%}
-
-\authorrunning{Farzin 2019} % if too long for running head
-\institute{}
-%\institute{F. Author \at
-%              first address \\
-%              Tel.: +123-45-678910\\
-%              Fax: +123-45-678910\\
-%              \email{bfarzin@gmail.com}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-%           \and
-%           S. Author \at
-%              second address
-%}
-
-\date{Received: 17 June 2019 / Accepted: date}
-% The correct dates will be entered by the editor
 
@@
 Twitter has slang and abbreviations that are unique to the short-format as well as generous use of emoticons.
-To capture these features, we collected our own dataset based on Spanish Tweets that is 16 times larger than the competition data set and allowed us to pre-train a langauge model.
+To capture these features, we collected our own dataset based on Spanish Tweets that is 16 times larger than the competition data set and allowed us to pre-train a language model.
 Humor is subtle and using a label smoothed loss allowed us to not become too overconfident in our predictions and train more quickly without the gradual unfreezing required by ULMFiT.
@@
 
-\section{other}
+\section{Acknowledgements}
+The author would like to thank Kyle Kastner for his edits, suggestions and recommendations in writing up these results.
 
-%%  Comment from Kyle:
-%%Maybe you have some good advice to give other people related to points one and two of your main contributions, what do you think the primary benefit of transfer learning was - especially the use of tweets for the vocab and so on, versus the "standard" wikipedia?
-%
-%Pretraining allows the model to get "close" to the right language model
-%Pre-training uses a wider universe of language than just the model training set.  We have a better chance to predict the test-set data by leveraging additional data.
-%
-%%As for the label smoothing, what is your general insight on what settings of label smoothing worked well, why penalizing confident stuff was extra useful here?	
-%%	For example in 4.2.1, why does label smoothing bypass gradual unfreezing? 
-%
-%With so many trainable params models can become focused on refining the prediiction on already correct predictions (going from .85 to .95 in the softmax output).
-Gradual unfreezing prevents this kind of over-fitting by regularizing through restricting the params that can be fit.
-Label smoothing achieves the same thing by preventing the maximum classification from becoming too large.
-%
-%Manually built labels always lead to some errors.
-there could be some that are only marginally funny, yet classified as "Humorous."  We don't want to be overconfident in our classification of these jokes,
-%and label smoothing helps us to overcome that noise. 
-%
-%
-%Twitter has slang and abbreviations that are unique to the short-format as well as generous use of emoticons.
-
-\begin{acknowledgements}
-The author would like to thank Kyle Kastner for his edits, suggestions and recommendations in writing up these results. 
-\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-%\bibliographystyle{fullname}      % basic style, author-year citations
-
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
+\bibliographystyle{splncs04}
 \bibliography{local}   % name your BibTeX data base

### 2019-06-19 prod/paper/newformat/paper_draft.tex
update with Janine revisions.  New title

@@
 
-\title{ULMFiT for Joke Classification in Spanish}
-
-\author{Bobak Farzin\inst{1}}
+%\title{Modified ULMFiT for Joke Classification in Spanish}
+\title{Applying a Pretrained Langague Model to Spanish Twitter Humor Prediction}
+\author{Bobak Farzin\\ June 2019}
 %
@@
 To overcome the inherent errors in some labels we reduce our class confidence with label smoothing in the loss function.
-All the code for our project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final} repository for easy reference and to enable replication by others.
+All the code for our project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final, Accessed on 19 June 2019} repository for easy reference and to enable replication by others.
 
@@
 - ?`Cobra?\\
-- No, gratis.\footnote{https://www.fluentin3months.com/spanish-jokes/}
+- No, gratis.\footnote{https://www.fluentin3months.com/spanish-jokes/, Accessed on 19 June 2019}
 \end{quote}
@@
 Thus, building a system to classify the humor of tweets is a difficult task.
-However, with transfer-learning and the Fastai library\footnote{https://docs.fast.ai/}, we can build a high quality classifier in a foreign language.
-Our system outperforms a Naive Bayes SVM baseline, which is frequently considered a "strong baseline" for many NLP related tasks \footnote{https://twitter.com/radamihalcea/status/1119020144389443585}.
+However, with transfer-learning and the Fastai library\footnote{https://docs.fast.ai/, Accessed on 19 June 2019}, we can build a high quality classifier in a foreign language.
+Our system outperforms a Naive Bayes Support Vector Machine (NBSVM) baseline, which is frequently considered a "strong baseline" for many Natural Language Processing (NLP) related tasks \footnote{https://twitter.com/radamihalcea/status/1119020144389443585, Accessed on 19 June 2019}.
 
@@
 \label{sec:task}
-The \textit{Humor Analysis based on Humor Annotation (HAHA) 2019}\cite{overview_haha2019} competition asked for analysis of two tasks in the Spanish language based on a corpus of publicly collected data ~\cite{castro2018crowd}:
+The \textit{Humor Analysis based on Humor Annotation (HAHA) 2019}\cite{overview_haha2019} competition asked for analysis of two tasks in the Spanish language based on a corpus of publicly collected data described in Castro et al.~\cite{castro2018crowd}:
 \begin{itemize}
 \item \textbf{Task1: Humor Detection}:Determine if a tweet is humorous. System ranking is based on F1 score which balances precision and accuracy.
-\item \textbf{Task2: Funniness Score}:If humorous, what is the average humor rating of the tweet? System ranking is based on RMSE.
+\item \textbf{Task2: Funniness Score}:If humorous, what is the average humor rating of the tweet? System ranking is based on root mean-squared error (RMSE).
 \end{itemize}
@@
 \label{sec:system}
-We generally follow the method of ULMFiT ~\cite{HowardRuder:DBLP:journals/corr/abs-1801-06146} including pre-training and differential learning rates. 
+We modify the method of Universal Langage Model Fine-tuning for Text Classification (ULMFiT) presented in Howard and Ruder~\cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}.
+The primary steps are:
 \begin{enumerate}
@@
 \subsection{Additional Data}
-We collected a corpus for our LM based on Spanish Twitter using tweepy~\cite{Tweepy} run for three 4 hours sessions and collecting any tweet with the terms 'el','su','lo','y' or 'en'.
+We collected a corpus for our LM based on Spanish Twitter using tweepy~\cite{Tweepy} run for three 4-hour sessions and collecting any tweet with the terms 'el','su','lo','y' or 'en'.
 We excluded retweets to minimize repeated examples in our language model training.
@@
 \subsection{Cleaning}
-We applied a list of default cleanup functions included in Fastat and added an additional one for this Twitter dataset.
-\begin{itemize}
-	\item Add spaces between special chars (ie. \verb|!!!| to \verb|! ! !|)
-	\item Remove useless spaces (remove more than 2 spaces in sequence)
+We applied a list of default cleanup functions in sequence.
+They are close to the standard cleanup included in the Fast.ai library with the addition of one for this Twitter dataset.
+Cleanup of data is key to expressing the data in a compact way so that the LM can keep the relevant current data when trying to predict the next work in a sequence.
+\begin{enumerate}
 	\item Replace repetition at the character level (ie. \verb|grrrreat| becomes \verb|g xxrep r 3 eat|)
@@
 	\item Deal with ALL CAPS words replacing with a token and converting to lower case.
+	\item Add spaces between special chars (ie. \verb|!!!| to \verb|! ! !|)
+	\item Remove useless spaces (remove more than 2 spaces in sequence)	
 	\item \textbf{Addition:} Move all text onto a single line by replacing new-lines inside a tweet with a reserved word (ie. \verb|\n| to \verb|xxnl|)
-\end{itemize} 
+\end{enumerate} 
 %\pagebreak  %move as needed to keep tweet text together
@@
 We train the LM using a 90/10 training/validation split, reporting the validation loss and accuracy of next-word prediction on the validation set.
-For the LM, we selected a AWD\_LSTM \cite{Merity:DBLP:journals/corr/abs-1708-02182} model included in Fastai with QRNN\cite{Bradbury:DBLP:journals/corr/BradburyMXS16} units, 2304 hidden-states, 3 layers and a softmax layer to predict the next-word.
+For the LM, we selected a ASGD Weight-Dropped Long Short Term Memory (AWD\_LSTM, described in Merity et al.\cite{Merity:DBLP:journals/corr/abs-1708-02182}) model included in Fastai.
+We replaced the typical Long Short Term Memory (LSTM) units with Quasi Recurrent Neural Network (QRNN, described in Bradbury et al.\cite{Bradbury:DBLP:journals/corr/BradburyMXS16}) units.
+Our network has 2304 hidden-states, 3 layers and a softmax layer to predict the next-word.
 We tied the embedding weights\cite{WeightTie:DBLP:journals/corr/PressW16} on the encoder and decoder for training.
@@
 
-Parameters used for training and finetuning are shown in Table \ref{tab:tab_training}.
+Parameters used for training and fine-tuning are shown in Table \ref{tab:tab_training}.
 For all networks we applied a dropout multiplier which scales the dropout used throughout the network.  We used the Adam optimizer with weight decay as indicated in the table.
@@
 Following the work of Smith\cite{Smith:DBLP:journals/corr/abs-1803-09820} we found the largest learning-rate that we could apply and then ran a one-cycle policy for a single epoch.
-We then ran subsequent training with one-cycle and lower learning rates indicated in Table \ref{tab:tab_training}.
+This largest weight is shown in Table \ref{tab:tab_training} under "Learning Rate." Subsequent training epochs were run with one-cycle and lower learning rates indicated in Table \ref{tab:tab_training} under "Continued Training."
 
@@
 	Learning Rate & 1 epoch at $5*10^{-3}$ & 5 epochs at $3*10^{-3}$ \\
-    Cont. Training & 15 epochs at $1*10^{-3}$ & 10 epochs at $1*10^{-4}$\\
+    Continued Training & 15 epochs at $1*10^{-3}$ & 10 epochs at $1*10^{-4}$\\
 	\noalign{\smallskip}\hline
@@
 \subsection{Classification and Regression Fitting}
-Again, following the play-book from \cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change pre-trained network head to a softmax or linear output layer (as appropriate for the transfer task) and then load the LM weights for the layers below.
+Again, following the play-book from Howard and Ruder\cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change pre-trained network head to a softmax or linear output layer (as appropriate for the transfer task) and then load the LM weights for the layers below.
 We train just the new head from random initialization, then unfreeze the entire network and train with differential learning rates.
@@
 We sample 20 random seeds (see more in section \ref{sec:rand_seeds}) to find the best initialization for our gradient descent search.
-From these samples, we select the best validation F1 metric or MSE for use in our test submission.
+From these samples, we select the best validation F1 metric or Mean Squared Error (MSE) for use in our test submission.
 \subsubsection{Classifier setup}  For the classifier, we have a hidden layer and softmax head.
-We over-sample the minority class to balance the outcomes for better training using SMOTE\cite{Chawla:2002:SSM:1622407.1622416}.
-Our loss is label smoothing\cite{Labelsmoothing:DBLP:journals/corr/PereyraTCKH17} of the flattened cross-entropy loss.
+We over-sample the minority class to balance the outcomes for better training using Synthetic Minority Oversampling Technique (SMOTE, described in Chawla et al.\cite{Chawla:2002:SSM:1622407.1622416}).
+Our loss is label smoothing as described in Pereyra et al.\cite{Labelsmoothing:DBLP:journals/corr/PereyraTCKH17} of the flattened cross-entropy loss.
 Gradual unfreezing allows us to avoid catastropic forgetting, focus each stage of training and preventing over-fitting of the parameters to the training cases.
 We take an alternative approach to regularization and in our experiments found that we got similar results with label smoothing but without the separate steps and learning rate refinement required of gradual unfreezing.
-\subsubsection{Regression setup}  For the regression task, we fill all \verb|#N/A| labels with scores of 0.  We add a hidden layer and linear output head and mean-squared-error (MSE) loss function.
+\subsubsection{Regression setup}  For the regression task, we fill all \verb|#N/A| labels with scores of 0.  We add a hidden layer and linear output head and MSE loss function.
 
@@
 \subsection{Results}
-Below in Table \ref{tab:tab_results} we layout three results from our submissions in the competition.
-The first is the baseline Naive Bayes SVM solution, with an F1 of 0.7548.
+Below in Table \ref{tab:tab_results} we give three results from our submissions in the competition.
+The first is the baseline NBSVM solution, with an F1 of 0.7548.
 Second is our first random seed selected for the classifier which produces a 0.8083 result.
-While better than the NB-SVM solution, we pick the best validation F1 from the 20 seeds we tried.
+While better than the NBSVM solution, we pick the best validation F1 from the 20 seeds we tried.
 This produced our final submission of 0.8099.
@@
 To capture these features, we collected our own dataset based on Spanish Tweets that is 16 times larger than the competition data set and allowed us to pre-train a language model.
-Humor is subtle and using a label smoothed loss allowed us to not become too overconfident in our predictions and train more quickly without the gradual unfreezing required by ULMFiT.
+Humor is subtle and using a label smoothed loss prevented us from becoming overconfident in our predictions and train more quickly without the gradual unfreezing required by ULMFiT.
 We have open-sourced all  code used in this contest to further enable research on this task in the future.
@@
 \section{Acknowledgements}
-The author would like to thank Kyle Kastner for his edits, suggestions and recommendations in writing up these results.
+The author would like to thank Kyle Kastner for his edits, suggestions and recommendations in writing up these results. However, any omissions or errors are those of the authors alone.
 

### 2019-06-22 prod/paper/newformat/paper_draft.tex
another draft of paper

@@
 \title{Applying a Pretrained Langague Model to Spanish Twitter Humor Prediction}
-\author{Bobak Farzin\\ June 2019}
+\author{Bobak Farzin \\June 2019}
 %
@@
 %
-\institute{	\email{bfarzin@gmail.com}}
+\institute{USF Data Institue WAMRI Visting Scholar	\email{bfarzin@gmail.com}}
 
@@
 \label{sec:task}
-The \textit{Humor Analysis based on Humor Annotation (HAHA) 2019}\cite{overview_haha2019} competition asked for analysis of two tasks in the Spanish language based on a corpus of publicly collected data described in Castro et al.~\cite{castro2018crowd}:
+The \textit{Humor Analysis based on Human Annotation (HAHA) 2019}\cite{overview_haha2019} competition asked for analysis of two tasks in the Spanish language based on a corpus of publicly collected data described in Castro et al.~\cite{castro2018crowd}:
 \begin{itemize}
@@
 \subsection{Classification and Regression Fitting}
-Again, following the play-book from Howard and Ruder\cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change pre-trained network head to a softmax or linear output layer (as appropriate for the transfer task) and then load the LM weights for the layers below.
+Again, following the play-book from Howard and Ruder\cite{HowardRuder:DBLP:journals/corr/abs-1801-06146}, we change the pre-trained network head to a softmax or linear output layer (as appropriate for the transfer task) and then load the LM weights for the layers below.
 We train just the new head from random initialization, then unfreeze the entire network and train with differential learning rates.
@@
 \section{Acknowledgements}
-The author would like to thank Kyle Kastner for his edits, suggestions and recommendations in writing up these results. However, any omissions or errors are those of the authors alone.
+The author would like to thank all the participants on the fast.ai forums \footnote{http://forums.fasta.ai} for their ideas and suggestions and Kyle Kastner for his edits, suggestions and recommendations in writing up these results.
 

### 2019-06-27 prod/paper/newformat/paper_draft.tex
adding Jeremy
Update paper with latest judge comments

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
 \documentclass[runningheads]{llncs}
-%
 \usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 \title{Applying a Pretrained Langague Model to Spanish Twitter Humor Prediction}
-\author{Bobak Farzin \\June 2019}
+\author{Bobak Farzin \inst{1} Piotr Czapla \inst{2} and Jeremy Howard \inst{3} \\June 2019}
 %
@@
 %
-\institute{USF Data Institue WAMRI Visting Scholar	\email{bfarzin@gmail.com}}
+\institute{USF Data Institue, WAMRI Visting Scholar \\
+		\email{bfarzin@gmail.com} \\
+		\and
+		n-waves
+\and  
+University of San Francisco \\ \email{j@fast.ai}}
 
@@
 However, with transfer-learning and the Fastai library\footnote{https://docs.fast.ai/, Accessed on 19 June 2019}, we can build a high quality classifier in a foreign language.
-Our system outperforms a Naive Bayes Support Vector Machine (NBSVM) baseline, which is frequently considered a "strong baseline" for many Natural Language Processing (NLP) related tasks \footnote{https://twitter.com/radamihalcea/status/1119020144389443585, Accessed on 19 June 2019}.
+Our system outperforms a Naive Bayes Support Vector Machine (NBSVM) baseline, which is frequently considered a "strong baseline" for many Natural Language Processing (NLP) related tasks (see
+Wang et al \cite{Wang:2012:BBS:2390665.2390688}).
 
@@
 The HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons), a binary humor label, the number of votes for each of five star ratings and a ``Funniness Score'' that is the average of the 1 to 5 star votes cast.
-Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/}.
+Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/ Accessed on 19 June 2019}.
 
@@
 \subsection{Additional Data}
-We collected a corpus for our LM based on Spanish Twitter using tweepy~\cite{Tweepy} run for three 4-hour sessions and collecting any tweet with the terms 'el','su','lo','y' or 'en'.
+We collected a corpus for our LM based on Spanish Twitter using tweepy~\footnote{http://github.com/tweepy/tweepy, Accessed on 19 June 2019} run for three 4-hour sessions and collecting any tweet with the terms 'el','su','lo','y' or 'en'.
 We excluded retweets to minimize repeated examples in our language model training.

### 2019-07-01 prod/paper/newformat/paper_draft.tex
update with latest revisions:

@@
 %\title{Modified ULMFiT for Joke Classification in Spanish}
-\title{Applying a Pretrained Langague Model to Spanish Twitter Humor Prediction}
+\title{Applying a Pre-trained Language Model to Spanish Twitter Humor Prediction}
 \author{Bobak Farzin \inst{1} Piotr Czapla \inst{2} and Jeremy Howard \inst{3} \\June 2019}
 %
-\authorrunning{Farzin 2019}
+\authorrunning{Farzin et al. 2019}
 % First names are abbreviated in the running head.
@@
 		\and
-		n-waves
+		n-waves\\
+		\email{Piotr.Czapla@n-waves.com}
 \and  
-University of San Francisco \\ \email{j@fast.ai}}
+University of San Francisco \& Fast.ai\\ \email{j@fast.ai}}
 
@@
 
-\keywords{First keyword \and Second keyword \and More}
+\keywords{Natural Language Processing \and Transfer Learning \and Sentiment Analysis \and Humor Classification}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 Thus, building a system to classify the humor of tweets is a difficult task.
-However, with transfer-learning and the Fastai library\footnote{https://docs.fast.ai/, Accessed on 19 June 2019}, we can build a high quality classifier in a foreign language.
+However, with transfer-learning and the Fast.ai library\footnote{https://docs.fast.ai/, Accessed on 19 June 2019}, we can build a high quality classifier in a foreign language.
 Our system outperforms a Naive Bayes Support Vector Machine (NBSVM) baseline, which is frequently considered a "strong baseline" for many Natural Language Processing (NLP) related tasks (see
@@
 Rather than hand-crafted language features, we have taken an "end to end" approach building from the raw text to a final model that achieves the tasks as presented.
-Our paper lays out the details of the system and our code can be found in a GitHub repo for use by other researchers to extend the state of the art in sentiment analysis.
+Our paper lays out the details of the system and our code can be found in a GitHub repository for use by other researchers to extend the state of the art in sentiment analysis.
 
@@
 \begin{enumerate}
-	\item Replace repetition at the character level (ie. \verb|grrrreat| becomes \verb|g xxrep r 3 eat|)
+	\item Replace more than 3 repetitions of the same character (ie. \verb|grrrreat| becomes \verb|g xxrep r 4 eat|)
 	\item Replace repetition at the word level (similar to above)
@@
 \subsection{Tokenization}
-We used sentencepiece~\cite{SentencePiece:DBLP:journals/corr/abs-1808-06226} to parse into sub-word units and reduce the possible out-of-vocabulary (OOV) terms in the data set.
-We selected a vocab size of 30,000 and used the byte-pair encoding (bpe) model.
+We used sentencepiece~\cite{SentencePiece:DBLP:journals/corr/abs-1808-06226} to parse into sub-word units and reduce the possible out-of-vocabulary terms in the data set.
+We selected a vocab size of 30,000 and used the byte-pair encoding (BPE) model.
+To our knowledge this is the first time that the BPE toenization has been used with ULMFiT in a competition model.
 
@@
 We train the LM using a 90/10 training/validation split, reporting the validation loss and accuracy of next-word prediction on the validation set.
-For the LM, we selected a ASGD Weight-Dropped Long Short Term Memory (AWD\_LSTM, described in Merity et al.\cite{Merity:DBLP:journals/corr/abs-1708-02182}) model included in Fastai.
+For the LM, we selected a ASGD Weight-Dropped Long Short Term Memory (AWD\_LSTM, described in Merity et al.\cite{Merity:DBLP:journals/corr/abs-1708-02182}) model included in Fast.ai.
 We replaced the typical Long Short Term Memory (LSTM) units with Quasi Recurrent Neural Network (QRNN, described in Bradbury et al.\cite{Bradbury:DBLP:journals/corr/BradburyMXS16}) units.
@@
 We train just the new head from random initialization, then unfreeze the entire network and train with differential learning rates.
+We layout our training parameters in Table \ref{tab:clas_training}.
 
@@
 With more exploration, a better seed could likely be found.
-Though we only use a single seed for the LM training, one could do a similar search with random seeds for LM pre-training, and further select the best down-stream seed similar to \cite{Poleval:DBLP:journals/corr/abs-1810-10222}
+Though we only use a single seed for the LM training, one could do a similar search with random seeds for LM pre-training, and further select the best down-stream seed similar to Czapla et al \cite{Poleval:DBLP:journals/corr/abs-1810-10222}.
 
@@
 \subsection{Results}
-Below in Table \ref{tab:tab_results} we give three results from our submissions in the competition.
+Table \ref{tab:tab_results} gives three results from our submissions in the competition.
 The first is the baseline NBSVM solution, with an F1 of 0.7548.
@@
 This produced our final submission of 0.8099.
+Note that our third place entry was 1.1\% worse in F1 score than first place but 1.2\% \textit{better} in F1 than the $4^{th}$ place entry.
 Note that applying this model over our validation set achieved an F1 of 0.8254 and a test set F1 of 0.8099 - a drop of 0.0155 in F1 for the true out-of-sample data.
@@
 \section{Acknowledgements}
-The author would like to thank all the participants on the fast.ai forums \footnote{http://forums.fasta.ai} for their ideas and suggestions and Kyle Kastner for his edits, suggestions and recommendations in writing up these results.
+The author would like to thank all the participants on the fast.ai forums \footnote{http://forums.fasta.ai} for their ideas and suggestions.
+Also, Kyle Kastner for his edits, suggestions and recommendations in writing up these results.
 

### 2019-07-03 prod/paper/newformat/paper_draft.tex
final draft of paper

@@
 \title{Applying a Pre-trained Language Model to Spanish Twitter Humor Prediction}
-\author{Bobak Farzin \inst{1} Piotr Czapla \inst{2} and Jeremy Howard \inst{3} \\June 2019}
+\author{Bobak Farzin \inst{1}$^{*}$ Piotr Czapla \inst{2}\thanks{BF was the primary researcher.
+PC contributed with suggestions for the random seeds as a hyper-parameters and label smoothing to speed up training.
+JH contributed with suggestion for higher dropout throughout the network for more generalization.} and Jeremy Howard\inst{3}$^{*}$ \\June 2019}
 %
@@
 \subsection{Additional Data}
-We collected a corpus for our LM based on Spanish Twitter using tweepy~\footnote{http://github.com/tweepy/tweepy, Accessed on 19 June 2019} run for three 4-hour sessions and collecting any tweet with the terms 'el','su','lo','y' or 'en'.
+We collected a corpus for our LM based on Spanish Twitter using tweepy~\footnote{http://github.com/tweepy/tweepy, Accessed on 19 June 2019} run for three 4-hour sessions and collecting any tweet with any of the terms 'el','su','lo','y' or 'en'.
 We excluded retweets to minimize repeated examples in our language model training.
-In total, we collected 475,143 tweets.
-This data set is nearly 16 times larger than the text provided by the competition alone.
-The frequency of terms, punctuation and vocabulary can be quite different from the standard Wikipedia corpus that is often used to train an LM from scratch.
+In total, we collected 475,143 tweets - a data set is nearly 16 times larger than the text provided by the competition alone.
+The frequency of terms, punctuation and vocabulary used on Twitter can be quite different from the standard Wikipedia corpus that is often used to train an LM from scratch.
 
@@
 \subsection{Cleaning}
-We applied a list of default cleanup functions in sequence.
-They are close to the standard cleanup included in the Fast.ai library with the addition of one for this Twitter dataset.
-Cleanup of data is key to expressing the data in a compact way so that the LM can keep the relevant current data when trying to predict the next work in a sequence.
+We applied a list of default cleanup functions in sequence (see list below).
+They are close to the standard clean-up included in the Fast.ai library with the addition of one function for the Twitter dataset.
+Cleanup of data is key to expressing information in a compact way so that the LM can use the relevant data when trying to predict the next word in a sequence.
 \begin{enumerate}
@@
 We train the LM using a 90/10 training/validation split, reporting the validation loss and accuracy of next-word prediction on the validation set.
-For the LM, we selected a ASGD Weight-Dropped Long Short Term Memory (AWD\_LSTM, described in Merity et al.\cite{Merity:DBLP:journals/corr/abs-1708-02182}) model included in Fast.ai.
+For the LM, we selected an ASGD Weight-Dropped Long Short Term Memory (AWD\_LSTM, described in Merity et al.\cite{Merity:DBLP:journals/corr/abs-1708-02182}) model included in Fast.ai.
 We replaced the typical Long Short Term Memory (LSTM) units with Quasi Recurrent Neural Network (QRNN, described in Bradbury et al.\cite{Bradbury:DBLP:journals/corr/BradburyMXS16}) units.
@@
 Our loss is label smoothing as described in Pereyra et al.\cite{Labelsmoothing:DBLP:journals/corr/PereyraTCKH17} of the flattened cross-entropy loss.
-Gradual unfreezing allows us to avoid catastropic forgetting, focus each stage of training and preventing over-fitting of the parameters to the training cases.
+In ULMFiT, gradual unfreezing allows us to avoid catastropic forgetting, focus each stage of training and preventing over-fitting of the parameters to the training cases.
 We take an alternative approach to regularization and in our experiments found that we got similar results with label smoothing but without the separate steps and learning rate refinement required of gradual unfreezing.
@@
 This produced our final submission of 0.8099.
-Note that our third place entry was 1.1\% worse in F1 score than first place but 1.2\% \textit{better} in F1 than the $4^{th}$ place entry.
-Note that applying this model over our validation set achieved an F1 of 0.8254 and a test set F1 of 0.8099 - a drop of 0.0155 in F1 for the true out-of-sample data.
+Our best model achieved an five-fold average F1 of 0.8254 on the validation set shown in Figure \ref{fig:random_seed_hist} but a test set F1 of 0.8099 - a drop of 0.0155 in F1 for the true out-of-sample data.
+Also note that our third place entry was 1.1\% worse in F1 score than first place but 1.2\% \textit{better} in F1 than the $4^{th}$ place entry.
 
+\setlength{\tabcolsep}{8pt}
 \begin{table}[ht]

### 2019-07-04 prod/paper/newformat/paper_draft.tex
fixing page number, footnotes, contributions

@@
-\documentclass[runningheads]{llncs}
+%\documentclass[runningheads]{llncs}
+\documentclass{llncs}
 \usepackage{graphicx}
+\pagenumbering{gobble}
 
@@
 
+{\let\thefootnote\relax\footnotetext{Copyright \textcopyright\ 2019 for this paper by its authors.
+Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).
+IberLEF 2019, 24 September 2019, Bilbao, Spain.
+}}
+
 %\title{Modified ULMFiT for Joke Classification in Spanish}
 \title{Applying a Pre-trained Language Model to Spanish Twitter Humor Prediction}
-\author{Bobak Farzin \inst{1}$^{*}$ Piotr Czapla \inst{2}\thanks{BF was the primary researcher.
-PC contributed with suggestions for the random seeds as a hyper-parameters and label smoothing to speed up training.
-JH contributed with suggestion for higher dropout throughout the network for more generalization.} and Jeremy Howard\inst{3}$^{*}$ \\June 2019}
+\author{Bobak Farzin \inst{1} Piotr Czapla \inst{2} and Jeremy Howard\inst{3} \\June 2019}
 %
@@
 %
-\institute{USF Data Institue, WAMRI Visting Scholar \\
+\institute{USF Data Institue, WAMRI Visting Scholar, USA \\
 		\email{bfarzin@gmail.com} \\
 		\and
-		n-waves\\
+		n-waves, Poland\\
 		\email{Piotr.Czapla@n-waves.com}
 \and  
-University of San Francisco \& Fast.ai\\ \email{j@fast.ai}}
+University of San Francisco \& Fast.ai, USA\\ \email{j@fast.ai}}
 
@@
 To overcome the inherent errors in some labels we reduce our class confidence with label smoothing in the loss function.
-All the code for our project is included in a GitHub\footnote{https://github.com/bfarzin/haha\_2019\_final, Accessed on 19 June 2019} repository for easy reference and to enable replication by others.
+All the code for our project is included in a GitHub\footnotemark[4] repository for easy reference and to enable replication by others.
 
@@
 - ?`Cobra?\\
-- No, gratis.\footnote{https://www.fluentin3months.com/spanish-jokes/, Accessed on 19 June 2019}
+- No, gratis.\footnotemark[5]
 \end{quote}
@@
 \end{quote}
+\pagebreak
+\footnotetext[4]{https://github.com/bfarzin/haha\_2019\_final, Accessed on 19 June 2019}
+\footnotetext[5]{https://www.fluentin3months.com/spanish-jokes/, Accessed on 19 June 2019}
+
 Humor does not translate well because it often relies on double-meaning or a subtle play on word choice, pronunciation, or context.
@@
 Thus, building a system to classify the humor of tweets is a difficult task.
-However, with transfer-learning and the Fast.ai library\footnote{https://docs.fast.ai/, Accessed on 19 June 2019}, we can build a high quality classifier in a foreign language.
+However, with transfer-learning and the Fast.ai library\footnote[6]{https://docs.fast.ai/, Accessed on 19 June 2019}, we can build a high quality classifier in a foreign language.
 Our system outperforms a Naive Bayes Support Vector Machine (NBSVM) baseline, which is frequently considered a "strong baseline" for many Natural Language Processing (NLP) related tasks (see
@@
 The HAHA dataset includes labeled data for 24,000 tweets and a test set of 6,000 tweets (80\%/20\% train/test split.)  Each record includes the raw tweet text (including accents and emoticons), a binary humor label, the number of votes for each of five star ratings and a ``Funniness Score'' that is the average of the 1 to 5 star votes cast.
-Examples and data can be found on the CodaLab competition webpage\footnote{http://competitions.codalab.org/competitions/22194/ Accessed on 19 June 2019}.
+Examples and data can be found on the CodaLab competition webpage\footnote[7]{http://competitions.codalab.org/competitions/22194/ Accessed on 19 June 2019}.
 
@@
 \subsection{Additional Data}
-We collected a corpus for our LM based on Spanish Twitter using tweepy~\footnote{http://github.com/tweepy/tweepy, Accessed on 19 June 2019} run for three 4-hour sessions and collecting any tweet with any of the terms 'el','su','lo','y' or 'en'.
+We collected a corpus for our LM based on Spanish Twitter using tweepy\footnote[8]{http://github.com/tweepy/tweepy, Accessed on 19 June 2019} run for three 4-hour sessions and collecting any tweet with any of the terms 'el','su','lo','y' or 'en'.
 We excluded retweets to minimize repeated examples in our language model training.
@@
 
+\section{Author Contributions}BF was the primary researcher.
+PC contributed with suggestions for the random seeds as a hyper-parameters and label smoothing to speed up training.
+JH contributed with suggestion for higher dropout throughout the network for more generalization.
+
 \section{Acknowledgements}
-The author would like to thank all the participants on the fast.ai forums \footnote{http://forums.fasta.ai} for their ideas and suggestions.
+The author would like to thank all the participants on the fast.ai forums \footnote[9]{http://forums.fasta.ai} for their ideas and suggestions.
 Also, Kyle Kastner for his edits, suggestions and recommendations in writing up these results.
